Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-26 sections/eval.tex
Update on Overleaf.

Sparse Matrix-Matrix Multiplication (SpGEMM) is a fundamental operation in scientific computing and data analytics. SpGEMM focuses on efficiently computing the product of two sparse matrices to produce an output sparse matrix.
The inner product, outer product, and Gustavson's method are three different approaches to performing SpGEMM. 
Inner product involves multiplying two matrices by taking dot products of corresponding rows and columns.
Outer product computes the product of all pairs of elements from the input matrices.

>>>>

Sparse Matrix-Matrix Multiplication (SpGEMM) is a fundamental operation in scientific computing and data analytics. SpGEMM focuses on efficiently computing the product of two sparse matrices to produce an output sparse matrix.
The inner product, outer product, and Gustavson's algorithm are three different approaches to performing SpGEMM. 
Inner product involves multiplying two matrices by taking dot products of corresponding rows and columns.
Outer product computes the product of all pairs of elements from the input matrices.

More detailed explanation is available in Section 2.2 of ~\cite{} \changwan{gamma}.
